---
title: RLadiesDC
output:
  rmarkdown::html_document:
    toc: true
    toc_depth: 6
---

```{r}
# ---
# title: Shiny - googlesheets Integration
# author: Mauro Lepore
# date: '2018-01-06'
# slug: shiny-googlesheets-integration
# categories:
#   - R
# tags:
#   - R
#   - Shiny
#   - googlesheets
#   - RLadiesDC
#   - meetup
# ---
```


```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
# hadley's settings
set.seed(1014)
options(digits = 3)

knitr::opts_chunk$set(
  eval = FALSE,
  echo = TRUE,  # {mine}
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  rows.print = 3  # {mine}
)
```

# Overview

This post shows one workflow that integrates two packages: [__shiny__](https://github.com/rstudio/shiny) and [__googlesheets__](https://github.com/jennybc/googlesheets). It is inspired by [this meetup](https://www.meetup.com/rladies-dc/events/245819613/) of [\@RLadiesDC](https://twitter.com/RLadiesDC), led by [Kelly O'Briant](https://twitter.com/b23kelly).

My goal is to build a web application to explore the dataframes of the __datasets__ package. Each dataset I'll push into a spreadsheet, and all spreadsheets will live in a single worksheet, called _datasets_. To save time I won't work the entire dataframes but only with their first few rows (their head).

```{r pkg}
library(googlesheets)
library(tidyverse)
library(datasets)
```

# Choose datasets

```{r dataframes}
all_nms <- ls("package:datasets")
all_dts <- all_nms %>% map(get) %>% set_names(all_nms)
dfm_list <- all_dts %>% keep(is.data.frame) %>% map(head)
```

# Create a worksheet and push each dataframe to one spreadsheets

```{r datasets_spreadsheet}
# Create a worksheet with an empty spreadsheet
dts <- gs_new("datasets")
```

```{r}
map2(
  .x = dfm_list, .y = names(dfm_list),
  ~gs_ws_new(dts, ws_title = .y, input = .x)
)
# Delete the empty spreadsheet created before
dts <- gs_ws_delete(dts, ws = 1)
```

Confirm that dataset is now lives one of my Google Sheets.

```{r}
gs_ls()[1, ]
```

Now I'm ready to build my shiny app.




